Home Nighttime Cough Monitoring

### 2025-07-17 Lilah Melzer/cough_monitor_analysis.qmd
added comorbidities to cough monitor

    cftr_mod, cftr_mod_type, mucolytic:antih, pulm_ex, contains("micro_type___")

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
t1 <- tableby(
  Diagnosis ~ nih_sex + age_at_consent + height_perc + weight_perc +
    nih_race + nih_ethnicity + cftr_mod + cftr_mod_type + Genotype + pre_fev_pp +
    total_sleep + pulm_ex + micro_type___1 + micro_type___2 + micro_type___3 +
    micro_type___4,
  data = demo, control = mycontrols
)
summary(t1, pfootnote = T)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
fig2 <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid)
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.2, aes(linetype = Diagnosis)) +
  geom_smooth(color = "black", aes(group = Diagnosis, linetype = Diagnosis)) +
  annotate("rect", xmin = 1, xmax = 29, ymin = 1, ymax = 275, alpha = 0.1) +
  annotate("rect", xmin = 41, xmax = 76, ymin = 1, ymax = 275, alpha = 0.1) +
  ylim(c(1, 275)) +
  xlim(c(0, 100)) +
  theme_bw() +
  scale_y_break(c(80, 265), scales = 0.25, ticklabels = c(265, 270, 275))
fig2
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
```

>>>>

    cftr_mod, cftr_mod_type, mucolytic:antih, pulm_ex, contains("comorbid_dx"),
    contains("micro_type___")

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
t1 <- tableby(
  Diagnosis ~ nih_sex + age_at_consent + height_perc + weight_perc +
    nih_race + nih_ethnicity + cftr_mod + cftr_mod_type + Genotype + pre_fev_pp +
    total_sleep + pulm_ex + comorbid_dx___1 + comorbid_dx___2 +
    comorbid_dx___3 + comorbid_dx___4 + comorbid_dx___5 + micro_type___1 +
    micro_type___2 + micro_type___3 + micro_type___4,
  data = demo, control = mycontrols
)
summary(t1, pfootnote = T)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
fig2 <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid)
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.2, aes(linetype = Diagnosis)) +
  geom_smooth(color = "black", aes(group = Diagnosis, linetype = Diagnosis)) +
  annotate("rect", xmin = 1, xmax = 29, ymin = 1, ymax = 275, alpha = 0.1) +
  annotate("rect", xmin = 41, xmax = 76, ymin = 1, ymax = 275, alpha = 0.1) +
  ylim(c(1, 275)) +
  xlim(c(0, 100)) +
  theme_bw() +
  scale_y_break(c(80, 265), scales = 0.25, ticklabels = c(265, 270, 275))
fig2
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
fig2_color <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid), color = Diagnosis
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.2, aes(linetype = Diagnosis)) +
  geom_smooth(aes(group = Diagnosis, linetype = Diagnosis)) +
  # annotate("rect", xmin = 1, xmax = 29, ymin = 1, ymax = 275, alpha = 0.1) +
  # annotate("rect", xmin = 41, xmax = 76, ymin = 1, ymax = 275, alpha = 0.1) +
  ylim(c(1, 275)) +
  xlim(c(0, 100)) +
  theme_bw() +
  scale_color_manual(values = c("#7570B3", "#D95F02")) +
  scale_y_break(c(80, 265), scales = 0.25, ticklabels = c(265, 270, 275))
fig2_color
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
```
